\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
fix confusion

In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
target device.  During this experiment, \tool disguised itself as a normal
keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
deployed to test the defense bypassing. We have tried to deploy the original
GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
outdated and cannot be executed at modern OS; so we have to home-brew a similar
defense mechanism based on its paper~\cite{tian2015defending}.  At the
beginning, our home-brewed version of GoodUSB asked victim to manually complete
a CAPTCHA to  authorize the new USB device, a.k.a our \tool. But at this time,
by the design of GoodUSB, \fengwei{The following sentence is hard to
understand.} our \tool can already perform limited keystroke to complete the
CAPTCHA and will be rejected only after the failure of authorization. With the
video feedback from \tool, the attacker successfully completes the CAPTCHA.  Up
to this point, the bypass of defense like GoodUSB is completed as our \tool
gains full function from the GoodUSB and becomes a trusted device. Then, our
\tool works similar to the original BadUSB, inserting keystroke to perform
arbitrary execution on the laptop. We tested three scripts, ranging from
reverse shell backdoor to malware payload execution, all of which resulting in
success.  With this experiment, we have proven the defense bypassing is succeed
using \tool.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

\fengwei{Explain the figure in the text.}
\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two power banks station products}
	\label{fig:PBS_products}
\end{figure}

>>>>

In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
target device.  During this experiment, \tool disguised itself as a normal
keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
deployed to test the defense bypassing. We have tried to deploy the original
GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
outdated and cannot be executed at modern OS; so we have to home-brew a similar
defense mechanism based on its paper~\cite{tian2015defending}.  At the
beginning, our home-brewed version of GoodUSB asked victim to manually complete
a CAPTCHA to  authorize the new USB device, a.k.a our \tool. But at this time,
by the design of GoodUSB, \fengwei{The following sentence is hard to
understand.}\hongyi{Fixed, removed redundant description} our \tool can already perform limited keystroke to complete the
CAPTCHA with video stream from \tool. Up
to this point, the bypass of defense like GoodUSB is completed as our \tool
gains full function from the GoodUSB and becomes a trusted device. Then, our
\tool works similar to the original BadUSB, inserting keystroke to perform
arbitrary execution on the laptop. We tested three scripts, ranging from
reverse shell backdoor to malware payload execution, all of which resulting in
success.  With this experiment, we have proven the defense bypassing is succeed
using \tool.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

\fengwei{Explain the figure in the text.}
\begin{figure}[t]
	\centering
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
	\caption{Two Power Bank Stations}
	\label{fig:PBS_products}
\end{figure}
